\mytitile\\~

### 2020-01-23 document.tex
additions from Lesha

	\begin{abstract}
	In this work, we irradiate a superconducting 
	artificial molecule composed of two 
	magnetic-flux-tunable transmons with 
	microwave light while monitoring its state 
	via joint dispersive readout. At certain 
	fluxes, the molecule demonstrates a complex 
	spectrum deviating qualitatively from the 
	solution of the Schrödinger equation without 
	driving. We reproduce the observed extra 
	spectral lines accurately by numerical 
	simulations, and find them to be a 
	consequence of an Autler-Townes-like effect 
	when a single tone is simultaneously dressing 
	the system and probing the transitions 
	between new eigenstates. We present 
	self-consistent analytical models accounting 
	both these processes at the same time that 
	agree well with both experiment and numerical 
	simulation. This study is an important step 
	towards understanding the behaviour of more 
	complex systems of many atoms interacting 
	with strong radiation.
	\end{abstract}

@@

Over the past twenty years, superconducting 
artificial atoms (SAAs) were used in numerous 
experiments in a compelling demonstration of the 
validity of fundamental quantum mechanical 
laws\cite{you2011atomic}. Due to synthetic nature 
of SAAs, their Hamiltonians can be pre-designed 
and engineered which makes them a particularly 
versatile tool for studies in quantum optics. 
Notably, high controllability of their parameters 
allows direct observation of novel physical 
effects previously inaccessible for natural 
systems.

One of the most prominent milestones that 
superconducting quantum circuits have reached so 
far is the strong coupling with light in {circuit 
QED}\cite{wallraff2004strong, 
chiorescu2004coherent} when the decoherence rates 
appear smaller than the Rabi frequency. 
Currently, they are surpassing all other 
implementations of strong coupling in terms of 
coherence\cite{forn2019ultrastrong}. 
However, in sharp contrast with natural atoms and 
molecules, SAAs do not even require confined 
radiation to implement strong coupling with 
light: they may be coupled unprecedently strongly 
to free-propagating electromagnetic waves in 1D 
on-chip waveguides\cite{astafiev2010resonance} 
without using cavities at all. The Rabi frequency 
in this case may reach 50\% of the transition 
frequency\cite{deng2015observation} which is even 
beyond strong coupling 
regime\cite{forn2019ultrastrong}. To correctly 
describe the behaviour of an atom in these 
conditions, the so-called \textit{dressed atom 
approach}\cite{cohen1998atom} is employed when 
the radiation has to be directly included in the 
Hamiltonian and affects its level structure.

So far, main experiments in on-chip quantum 
optics with intense propagating light were 
focused on single artificial 
atoms\cite{baur2009measurement, 
sillanpaa2009autler, astafiev2010resonance, 
novikov2013autler, suri2013observation, 
koshino2013observation, 
braumuller2015multiphoton, peng2018vacuum, 
gasparinetti2019two}. In all these works, light 
dressing of the atom manifests itself through 
Mollow triplets or Autler-Townes splittings of 
different kinds. However, despite the recent 
successes in control of large arrays of 
interacting SAAs\cite{Song574, ye2019propagation, 
arute2019quantum}, there were, up to our best 
knowledge, no experiments concerning interaction 
of such composite structures with intense free 
radiation. While there were studies on dressing 
of multi-atomic systems in a 
cavity\cite{fink2009dressed, 
macha2014implementation, shulga2017observation, 
yang2018probing}, their interaction with free 
radiation is no less attractive since its 
frequency may be easily tuned to observe various 
absorption processes for arbitrary configurations 
of the system parameters.

In this work, we study a pair of strongly coupled 
artificial atoms: a superconducting artificial 
molecule\cite{kou2017fluxonium} (SAM). We use two 
Xmon-type\cite{barends2013coherent} 
transmons\cite{koch2007charge} interacting with 
each other through a cavity 
bus\cite{majer2007coupling}. Microwave radiation 
is applied to this system through an on-chip 
coplanar waveguide while its state can be 
monitored by joint dispersive readout using the 
same coupling cavity\cite{chow2010detecting}. We 
find that strong interaction with microwaves not 
only calls forth multiphoton transitions of 
various orders between SAM states, but also 
significantly modifies its level structure. Even 
in a simple diatomic molecule, this leads to 
complex Autler-Townes-like effects involving 
single- and multiphoton  transitions that can 
only be explained in the dressed picture. We note 
that although the A-T splittings have been 
investigated before in a wide range of quantum 
systems (including natural 
molecules\cite{tamarat1995pump, 
ahmed2012autler}), we find qualitatively new 
spectral manifestations of light dressing when 
SAAs are irradiated unequally. We note that there 
were no such experiments with natural molecules, 
which could in principle demonstrate same 
effects, because they lack controllability and 
coherence of superconducting quantum devices, and 
previous studies of SAAs and free radiation have 
either involved just a single atom or have 
demonstrated only the standard spectral 
signatures known from the quantum optics (see 
Appendix \ref{sec:3-level-at}).

@@

\subsection{Device design and control}
We have designed the SAM as a pair of transmon 
(Xmon) SAAs with asymmetric 
SQUIDs\cite{hutchings2017tunable} ($E^1_{J, 
\sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
$E^{1,2}_C/h = 220$ MHz, $d^{1,2} =0.75$) coupled 
to a single notch-type\cite{probst2015efficient} 
$\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
1/100\ \text{ns}^{-1}$) which both 
couples\cite{majer2007coupling} the transmons and 
allows joint\cite{chow2010detecting} readout of 
their states. In \autoref{fig:experiment}~(a), 
the optical photograph of the device is shown 
depicting the layout of the components. The 
resonator in its upper part is connected to a 
coplanar waveguide through which the readout is 
performed. In its lower part, it is coupled to 
the transmons by a dual 
``claw''\cite{barends2013coherent} coupler. Flux 
lines that allow independent control of the 
transmon frequencies are coming from the sides. 
Finally, the excitation waveguide coming from 
below directs microwave signal towards the SAM. 
In \autoref{fig:experiment}~(b), the equivalent 
electrical circuit of the device is shown. The 
resonator fundamental mode is approximated as an 
LC-circuit (in the middle), the transmons are 
shown in colour on the sides; their SQUIDs are 
represented as tunable Josephson junctions. A 
capacitively coupled excitation line is also 
shown in green. Finally, in 
\autoref{fig:experiment}~(c) we show 
schematically the frequencies of the transmons 
depending on electric current $I$ which we apply 
to an external coil wound around the sample 
holder. Since the effective junction of the first 
transmon is larger, its spectrum (orange) lies 
higher in frequency than the spectrum of the 
second transmon (blue). Using individual 
flux-control lines, it is possible to align the 
SAAs so that the lower sweet-spot of the orange 
transmon is just below the upper sweet-spot of 
the blue transmon (see the dashed rectangle,  
\autoref{fig:experiment}~(c)). This configuration 
is, as we will show in the following, convenient 
to track the energies of highly excited levels 
via multi-photon transitions in a single 
spectroscopic scan. Additionally, the transmons 
are better protected from the flux noise in this 
area being close to their sweet spots.

@@

Having settled the naming system, we continue to 
analyse the plots. Due to the strong driving, we 
observe several multiphoton transitions besides 
the main lines at $\omega_{(1,2)}(I)/2\pi$ (or 
$01$ and $10$ lines). The ${02/2}$ and ${20/2}$ 
are very commonly found for transmons and lie 
$|\alpha_{(1,2)}|/2$ lower than the main lines 
$\omega_{(1,2)}(I)$. Another two-photon process 
appears as $11/2$ line when two SAAs are excited 
simultaneously. This process is used, for 
example, for doing the bSWAP 
gate\cite{poletto2012entanglement}; in our case, 
it is taking part in formation of feature I. A 
three-photon process $12/3$ is also clearly 
visible just below the $02/2$ line. As we will 
see, it is involved in forming features II and 
III. Notably, transitions $11/2$, ${21/3}$ and 
${12/3}$ are forbidden when there is no 
interaction between transmons ($J=0$). Therefore, 
it is expected that all Roman-numbered features 
should only appear with non-vanishing $\hat 
H_{int}$.

@@

From \autoref{fig:two-tone}~(d) we conclude that 
avoided crossing in III is between two 
transitions: ${12/3}$ and ${10} - {02}$ 
($\ket{10}\rightarrow\ket{02}$) which are of the 
same frequency when $\omega_1 = 
\omega_2+\alpha_2/2$. The latter process depopulating $01$ is better discernible in \autoref{fig:two-tone}~(d) 
than in \autoref{fig:two-tone}~(a), (b). For II, the 
opposite is true: ${21/3}$ and ${01} - {20}$ are 
crossing when $\omega_2 = \omega_1+\alpha_1/2$. 
From additional measurements and simulations, we 
find that the splitting depends on the driving 
power; the experimental and simulated results for 
II are shown in colour in \autoref{fig:zoom}~(a), (b), respectively. As one can see, the growth of the splitting with 
increasing power is linear: it is roughly equal 
to the FWHM of the ${01}$ spectral line. To fully 
quantify the shape of this splitting, in Section 
\ref{sec:theory} we derive analytical expressions 
for the dashed curves fitting the spectral lines 
in \autoref{fig:zoom}. In \autoref{fig:zoom}~(c), blue points, we present splitting sizes extracted by fitting of the model to the data as in \autoref{fig:zoom}~(a) for various power values of the microwave generator connected to the excitation waveguide. As one can see from the linear approximation of the points, the splitting indeed is simply proportional to the RMS voltage of the signal. From the model, we expect that the minimal distance between curves in the anticrossing is equal to $\frac{2\sqrt{3}}{3} \Omega_2$; using this relation, we extract the proportionality coefficient between $\Omega_2$ and $V_{rms}$ is around $0.23$ MHz/mV from the linear fit.

In \autoref{fig:difdrive}, we demonstrate a similar power dependence of feature I: increasing drive amplitude on one of the 
transmons while keeping the other one small and 
constant again elicits avoided crossings with the 
proportional size. We  show only the simulation results; an experiment is not possible with our sample because, since we have just a single excitation line, there is 
no way for us to control the driving amplitudes 
$\Omega_{1,2}$ individually. We note that two 
qualitatively different patterns arise depending 
on which of the transmons is driven stronger than 
the other. From this and from the shape of the 
splitting in feature I of 
\autoref{fig:two-tone}~(a), we can infer that 
$\Omega_1/\Omega_2 \approx 2$ there (also 
consistent with the 01, 10 linewidths in 
\autoref{fig:two-tone}~(c)). If in contrast both transmons are driven with equal amplitudes, the avoided crossing vanishes. As can be seen from black dashed lines in \autoref{fig:difdrive}, all these cases are explained well by our analytical model described in detail in Sections \ref{sec:theory} and \ref{sec:münchhausen}}.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{main_scheme_2}  
	\caption{Explaining feature III. \textbf{(a)} 
	Schematic of the transition frequencies near 
	III (not to scale). Red dashed line shows the 
	current (0.36 mA) where the first transmon 
	(orange) is below the second one (blue) 
	exactly by $\alpha_2/2$ and several 
	transitions become resonant. Here we assume 
	that each transmon is driven at its own 
	frequency. \textbf{(b)} System level 
	structure at the resonant point and the first transmon 
	driving of amplitude $\Omega_1$ 
	(orange ellipses) at a small detuning 
	$\Delta_1$ from $\omega_1$. The second 
	transmon driving is not shown here. Action of 
	$\hat H_{int}$ in RWA is depicted as 
	orange-blue circles. \textbf{(c)} In the 
	frame rotating with $\hat 
	H_{d}^1$, states $\ket{0j},\ket{1j}$ 
	become nearly degenerate ($\omega_1 
	\rightarrow \Delta_1$). Dressing increases this splitting to 
	$\Omega_1^R = \sqrt{\Omega_1^2 + 
	\Delta_1^2}$. \textbf{(d)} Transitions in the 
	dressed system induced by $\hat 
	H_{d}^2$ (coupled level subspaces are shown with blue ellipses). In 
	the left part of the panel, all possible 
	two-photon transitions near $\omega_1$ are 
	depicted: the blue transitions are not 
	shifted in frequency, the light blue ones are shifted 
	by $\pm\Omega^R_1/2$. In the right 
	part, the most contributing trajectories are 
	depicted; gray crosses show transitions that 
	are forbidden without the coupling $J$.}
	\label{fig:main_scheme}
\end{figure}

@@

In \autoref{fig:main_scheme}, we elaborate on which transitions
are involved in the A-T-like effect for feature III. 
For simplicity, we will temporarily assume that 
each transmon is driven at its own frequency 
(this assumption will be lifted in the following 
section). For convenience, in 
\autoref{fig:main_scheme}~(a) we schematically 
reproduce the transitions near III where the 
first transmon (orange) is below the second 
(blue), and the resonance point in current is 
shown with a dashed red line. Next, 
\autoref{fig:main_scheme}~(b) demonstrates the 
level structure of the SAM at 0.36 mA. Detuned by 
$\Delta_1$ from $10$, single-photon driving of 
$\hat H_d^1$ is shown with orange ellipses while 
much weaker two-photon $\hat H_d^2$ is not shown 
yet. Since from numerical simulations we know 
that the third level of the first transmon is not 
necessary to observe the splitting, $\ket{20}$ is 
shown transparent, and states $\ket{21},\ 
\ket{22}$ are not shown.

@@

\paragraph{Features II, III.} We start again with feature III. As shown in 
\autoref{fig:main_scheme}~(d), the sideband 
transitions are formed by two-photon processes 
with $\hat H_d^2$. On the other hand, we know from 
the unperturbed solution that in the laboratory 
frame the two transitions forming the avoided 
crossing are $10 - 02$ (one-photon) and $12/3$ 
(three-photon). This means that there should be a 
smooth transformation between these 1-, 2- and 3-photon 
processes when the system approaches the resonant 
point where $\alpha_2 + 2 \omega_{2} = 2\omega_1$. Let us consider hypothetical two-photon transitions $(10 
- 02)/2$ and $12/2$. In the frame rotating with 
the first transmon like in 
\autoref{fig:main_scheme}~(c) when $\Omega_1$ = 
0, their 
frequencies are
\begin{equation}
\begin{aligned}
\omega_{(10-02)/2} &= (\alpha_2 + 2 \omega_{2} - \Delta_1)/2,\\
 \omega_{12/2} &= (\alpha_2 + 2 \omega_{2} + \Delta_1)/2.
\end{aligned}
\end{equation}
When the first transmon becomes dressed by $\Omega_1 \neq 0$, its splitting $\Delta_1$ changes to $\Omega^R_1 =\sqrt{\Omega_{1}^2 + \left(\omega_{1} - \omega_{d}\right)^{2}}$. Substituting this new splitting into the equations above we find that $\omega_{(10-02)/2}$ and $\omega_{12/2}$ are exactly equal to the two-photon sideband frequencies $\omega_1 \pm \Omega_1^R/2$ established in the previous section. Therefore, it is logical to use them to model the splitting behaviour beyond the resonant point.

@@

When $\Omega_1 = 0$, these equations yield indentical pairs of solutions due to the properties of the modulus $|\omega_1 - \omega_d|$. Intriguingly, they are the three-photon and single-photon transition frequencies in the laboratory frame
\begin{equation}
\omega_d = \begin{cases} \frac{\alpha_2}{3} + \frac{2 \omega_{2}}{3} + \frac{\omega_{1}}{3}, \\ \alpha_2 + 2 \omega_{2} - \omega_{1}.\end{cases}
\end{equation}
When $\Omega_1 \neq 0$, we obtain the following solutions:
\begin{equation}
\omega_d = \frac{2 \alpha_2}{3} + \frac{4 \omega_{2}}{3} - \frac{\omega_{1}}{3} \pm \frac{\sqrt{3 \Omega_{1}^{2} + \left( \alpha_2 + 2 (\omega_{2} - \omega_{1})\right)^{2}}}{3}.
\label{eq:splitting_model}
\end{equation}
The minimal splitting between these lines is 
found at the resonant point and equals $\frac{2 
\sqrt{3}}{{3}} \Omega_1$. All these calculations 
can be repeated exactly for the feature II by 
swapping the transmons; in that case, the 
splitting will be $\frac{2 \sqrt{3}}{{3}} 
\Omega_2$.

@@

Continuing this logic, we can write down the resonance condition in the doubly-rotating frame when both transmons are dressed simultaneously:
\begin{equation}
\Omega_1^R \pm \Omega_2^R = 0.
\label{eq:zero-photon}
\end{equation}
Solving it for $\omega_d$, we obtain the 
generalization of \autoref{eq:topo_1} and 
\autoref{eq:topo_1_inv}:
\begin{equation}
\omega_d = \frac{\omega_{1} - \omega_{2}}{2} + \frac{\Omega_{1}^{2} - \Omega_{2}^{2}}{ 2\left(\omega_{1} - \omega_{2}\right)}
\label{eq:topo_comm}
\end{equation}

@@

\section{Standard Autler-Townes effect for a three-level atom} \label{sec:3-level-at}

@@

The choice of zero-order state vectors $\ket{N^0}$ from a degenerate subspace is arbitrary because any linear combination of basis vectors $\ket{n}$ from this subspace will satisfy the unperturbed Schrödinger equation. However, if we demand the \textit{change} of $\ket{N^0}$ to be small under the perturbation $\hat V$, they become determined and are given by diagonalization of $\hat V$ in the degenerate subspace. Unfortunately, $\hat V$ is zero in both our subspaces, so technically any choice of zero-order states will diagonalize $\hat V$. In other words, the degeneracy is not lifted in the first-order, and thus we have diagonalize the matrix\cite{landau2013quantum}
\begin{equation}
	M_{nn'} = \sum\limits_{m}\frac{V_{ nm}V_{mn^\prime}}{E_n-E_m}.
\end{equation}
Here, $\ket{n}$ and $\ket{n'}$ are the basis 
states from the degenerate subspace with energy 
$E_n$, and $V_{mn} = \bra{m} \hat  V \ket{n}$. 
The sum is over all other zero-order states 
$\ket{m}$ outside the degenerate subspace.

>>>>

	\begin{abstract}
	In this work, we irradiate a superconducting 
	artificial molecule composed of two 
	magnetic-flux-tunable transmons with 
	microwave light while monitoring its state 
	via joint dispersive readout. At certain 
	fluxes, the molecule demonstrates a complex 
	spectrum deviating qualitatively from the 
	solution of the Schrödinger equation without 
	driving. We reproduce the observed extra 
	spectral lines accurately by numerical 
	simulations, and find them to be a 
	consequence of an Autler-Townes-like effect 
	when a single tone is simultaneously dressing 
	the system and probing the transitions 
	between new eigenstates. We present 
	self-consistent analytical models accounting 
	both these processes at the same time that 
	agree well with both experiment and numerical 
	simulation. This study is an important step 
	towards understanding the behaviour of complex
	systems of many atoms interacting	with strong radiation.
	\end{abstract}

@@

Over the past twenty years, superconducting 
artificial atoms (SAAs) were used in numerous 
experiments in a compelling demonstration of the 
validity of fundamental quantum mechanical 
laws. Due to synthetic nature 
of SAAs, their Hamiltonians can be pre-designed 
and engineered which makes them a particularly 
versatile tool for studies in microwave quantum 
optics \cite{you2011atomic,Qopt_1300refs}. Notably, high controllability
of their parameters allows direct observation of novel physical 
effects previously inaccessible for natural 
systems.

One of the most prominent milestones that 
superconducting quantum circuits have reached so 
far is the strong coupling with light in {circuit 
QED}\cite{wallraff2004strong, 
chiorescu2004coherent} when the relaxation and decoherence rates 
appear smaller than the Rabi frequency. 
Currently, they are surpassing all other 
implementations of strong coupling in terms of 
coherence\cite{forn2019ultrastrong}. 
However, in sharp contrast with natural atoms and 
molecules, SAAs do not even require confined 
radiation to implement strong coupling with 
light: they may be coupled unprecedently strongly 
to free-propagating electromagnetic waves in 1D 
on-chip waveguides\cite{astafiev2010resonance} 
without using cavities at all. The Rabi frequency 
in this case may reach 50\% of the transition 
frequency\cite{deng2015observation} which is even 
beyond strong coupling 
regime\cite{forn2019ultrastrong}. To correctly 
describe the behaviour of an atom in these 
conditions, the so-called \textit{dressed atom 
approach}\cite{cohen1998atom} is employed when 
the radiation has to be directly included in the 
Hamiltonian and affects its level structure.

So far, experiments with intense driving fields resulting in the dressing effects in on-chip quantum optics  were 
focused on single artificial 
atoms\cite{baur2009measurement, 
sillanpaa2009autler, astafiev2010resonance, 
novikov2013autler, suri2013observation, 
koshino2013observation, 
braumuller2015multiphoton, peng2018vacuum, 
gasparinetti2019two}. In all these works, light 
dressing of the atom manifests itself through 
Mollow triplets or Autler-Townes (A-T) splittings of 
different kinds. However, despite the recent 
successes in control of large arrays of 
interacting SAAs\cite{Song574, ye2019propagation, 
arute2019quantum}, there were, up to our best 
knowledge, no experiments concerning interaction 
of similar composite structures with intense driving field. While there were studies on dressing 
of multi-atomic systems in a 
cavity\cite{fink2009dressed, 
macha2014implementation, shulga2017observation, 
yang2018probing}, their interaction with external dressing field is not less attractive since its 
frequency may be easily tuned to observe various 
absorption processes for arbitrary configurations 
of the system parameters.

In this work, we study a pair of strongly coupled 
artificial atoms: a superconducting artificial 
molecule\cite{kou2017fluxonium} (SAM). We use two 
Xmon-type\cite{barends2013coherent} 
transmons\cite{koch2007charge} interacting with 
each other through a cavity 
bus\cite{majer2007coupling}. Microwave radiation 
is applied to this system through an on-chip 
coplanar antenna while its state can be 
monitored by joint dispersive readout using the 
same coupling cavity\cite{chow2010detecting}. We 
find that strong interaction with microwaves not 
only results in multiphoton transitions of 
various orders between SAM states, but also 
significantly modifies its level structure. Even 
in a simple diatomic molecule, this leads to 
complex Autler-Townes-like effects involving 
single- and multiphoton  transitions that can 
only be explained in the dressed picture. We note 
that although the A-T splittings have been 
investigated before in a wide range of quantum 
systems (including natural 
molecules\cite{tamarat1995pump, 
ahmed2012autler}), we find qualitatively new 
spectral manifestations of light dressing when 
SAAs are irradiated unequally. We note that there 
were no such experiments with natural molecules, 
which could in principle demonstrate same 
effects, because they lack controllability and 
coherence of superconducting quantum devices, and 
previous studies of SAAs under strong driving field 
either involved just a single atom or have 
demonstrated only the standard spectral 
signatures known from the quantum optics (see 
Appendix \ref{sec:3-level-at}).

@@

\subsection{Device design and control}
We have designed the SAM as a pair of transmon 
(Xmon) SAAs with asymmetric 
SQUIDs\cite{hutchings2017tunable} ($E^1_{J, 
\sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
$E^{1,2}_C/h = 220$ MHz, $d^{1,2} =0.75$) coupled 
to a single notch-type\cite{probst2015efficient} 
$\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
1/100\ \text{ns}^{-1}$) which both 
couples\cite{majer2007coupling} the transmons and 
allows joint readout \cite{chow2010detecting} of 
their states. In \autoref{fig:experiment}~(a), 
the optical photograph of the device is shown, where the layout of the components is presented. The 
resonator in its upper part is connected to a 
coplanar waveguide through which the readout is 
performed. In its lower part, it is coupled to 
the transmons by a dual 
``claw''\cite{barends2013coherent} coupler. Flux 
lines that allow independent control of the 
transmon frequencies are coming from the sides. 
Finally, the excitation waveguide coming from 
below directs microwave signal towards the SAM. 
In \autoref{fig:experiment}~(b), the equivalent 
electrical circuit of the device is shown. The 
resonator fundamental mode is approximated as an 
LC-circuit (in the middle), the transmons are 
shown in color on the sides; their SQUIDs are 
represented as tunable Josephson junctions. A 
capacitively coupled excitation line is also 
shown in green. Finally, in 
\autoref{fig:experiment}~(c) we show 
schematically the frequencies of the transmons 
depending on electric current $I$ which we apply 
to an external coil wound around the sample 
holder. Since the effective junction of the first 
transmon is larger, its spectrum (orange) lies 
higher in frequency than the spectrum of the 
second transmon (blue). Using individual 
flux-control lines, it is possible to align the 
SAAs so that the lower sweet-spot of the orange 
transmon is just below the upper sweet-spot of 
the blue transmon (see the dashed rectangle,  
\autoref{fig:experiment}~(c)). This configuration 
is, as we will show in the following, convenient 
to track the energies of highly excited levels 
via multi-photon transitions in a single 
spectroscopic scan. Additionally, the transmons 
are better protected from the flux noise in this 
area being close to their sweet spots.

@@

Having settled the naming system, we continue to 
analyse the plots. Due to the strong driving, we 
observe several multiphoton transitions besides 
the main lines at $\omega_{(1,2)}(I)/2\pi$ (or 
$01$ and $10$ lines). The ${02/2}$ and ${20/2}$ 
are very commonly found for transmons and lie 
$|\alpha_{(1,2)}|/2$ lower than the main lines 
$\omega_{(1,2)}(I)$. Another two-photon process 
appears as $11/2$ line when two SAAs are excited 
simultaneously. This process is used, for 
example, for doing the bSWAP 
gate\cite{poletto2012entanglement}; in our case, 
it is taking part in formation of feature I. A 
three-photon process $12/3$ is also clearly 
visible just below the $02/2$ line. As we will 
see, processes $12/3$~and~$21/3$ are involved in forming features III and II, respectively. Notably, transitions $11/2$, ${21/3}$ and 
${12/3}$ are forbidden when there is no 
interaction between transmons ($J=0$). Therefore, 
it is expected that all Roman-numbered features 
should only appear with non-vanishing $\hat 
H_{int}$.

@@

From \autoref{fig:two-tone}~(d) we conclude that 
avoided crossing in III is between two 
transitions: ${12/3}$ (three-photon transition $\ket{00}\rightarrow\ket{12}$) and ${10} - {02}$ 
($\ket{10}\rightarrow\ket{02}$) which are of the 
same frequency when $\omega_1 = 
\omega_2+\alpha_2/2$. The latter process is depopulating $10$ and it is better discernible in \autoref{fig:two-tone}~(d) 
than in \autoref{fig:two-tone}~(a), (b). For II, the 
opposite is true: ${21/3}$ and ${01} - {20}$ are 
crossing when $\omega_2 = \omega_1+\alpha_1/2$. 
From additional measurements and simulations, we 
find that the splitting depends on the driving 
power; the experimental and simulated results for 
II are shown in colour in \autoref{fig:zoom}~(a), (b), respectively. As one can see, the growth of the splitting with 
increasing power is linear: it is roughly equal 
to the FWHM of the ${01}$ spectral line. To fully 
quantify the shape of this splitting, in Section 
\ref{sec:theory} we derive analytical expressions 
for the dashed curves fitting the spectral lines 
in \autoref{fig:zoom}. In \autoref{fig:zoom}~(c), blue points, we present splitting sizes extracted by fitting of the model to the data as in \autoref{fig:zoom}~(a) for various power values of the microwave generator connected to the excitation waveguide. As one can see from the linear approximation of the points, the splitting indeed is simply proportional to the RMS voltage of the signal. From the model, we expect that the minimal distance between curves in the anticrossing is equal to $\frac{2\sqrt{3}}{3} \Omega_2$; using this relation, we extract the proportionality coefficient between $\Omega_2$ and $V_{rms}$ is around $0.23$ MHz/mV from the linear fit.

In \autoref{fig:difdrive}, we demonstrate a similar power dependence of feature I: increasing drive amplitude on one of the 
transmons while keeping the other one small and 
constant again elicits avoided crossings with the 
proportional size. We  show only the simulation results; an experiment is not possible with our sample because, since we have just a single excitation line, there is 
no way for us to control the driving amplitudes 
$\Omega_{1,2}$ individually. We note that two 
qualitatively different patterns arise depending 
on which of the transmons is driven stronger than 
the other. From this and from the shape of the 
splitting in feature I of 
\autoref{fig:two-tone}~(a), we can infer that 
$\Omega_1/\Omega_2 \approx 2$ there (also 
consistent with the 01, 10 linewidths in 
\autoref{fig:two-tone}~(c)). If in contrast both transmons are driven with equal amplitudes, the avoided crossing vanishes. As can be seen from black dashed lines in \autoref{fig:difdrive}, all these cases are explained well by our analytical model described in detail in Sections \ref{sec:theory} and \ref{sec:münchhausen}.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{main_scheme_2}  
	\caption{Explaining feature III. \textbf{(a)} 
	Schematic of the transition frequencies near 
	III (not to scale). Black dashed line shows the 
	current (0.36 mA) where the first transmon 
	(orange) is below the second one (blue) 
	exactly by $\alpha_2/2$ and several 
	transitions become resonant. Here we assume 
	that each transmon is driven at its own 
	frequency. \textbf{(b)} System level 
	structure at the resonant point and the first transmon 
	driving of amplitude $\Omega_1$ 
	(orange ellipses) at a small detuning 
	$\Delta_1$ from $\omega_1$. The second 
	transmon driving is not shown here. Action of 
	$\hat H_{int}$ in RWA is depicted as 
	orange-blue circles. \textbf{(c)} In the 
	frame rotating with $\hat 
	H_{d}^1$, states $\ket{0j},\ket{1j}$ 
	become nearly degenerate ($\omega_1 
	\rightarrow \Delta_1$). Dressing increases this splitting to 
	$\Omega_1^R = \sqrt{\Omega_1^2 + 
	\Delta_1^2}$. \textbf{(d)} Transitions in the 
	dressed system induced by $\hat 
	H_{d}^2$ (coupled level subspaces are shown with blue ellipses). In 
	the left part of the panel, all possible 
	two-photon transitions near $\omega_1$ are 
	depicted: the blue transitions are not 
	shifted in frequency, the light blue ones are shifted 
	by $\pm\Omega^R_1/2$. In the right 
	part, the most contributing trajectories are 
	depicted; gray crosses show transitions that 
	are forbidden without the coupling $J$.}
	\label{fig:main_scheme}
\end{figure}

@@

In \autoref{fig:main_scheme}, we elaborate on which transitions
are involved in the A-T-like effect for feature III. 
For simplicity, we will temporarily assume that 
each transmon is driven at its own frequency 
(this assumption will be lifted in the following 
section). For convenience, in 
\autoref{fig:main_scheme}~(a) we schematically 
reproduce the transitions near III where the 
first transmon (orange) is below the second 
(blue), and the resonance point in current is 
shown with a dashed black line. Next, 
\autoref{fig:main_scheme}~(b) demonstrates the 
level structure of the SAM at 0.36 mA. Detuned by 
$\Delta_1$ from $10$, single-photon driving of 
$\hat H_d^1$ is shown with orange ellipses while 
much weaker two-photon $\hat H_d^2$ is not shown 
yet. Since from numerical simulations we know 
that the third level of the first transmon is not 
necessary to observe the splitting, $\ket{20}$ is 
shown transparent, and states $\ket{21},\ 
\ket{22}$ are not shown.

@@

\paragraph{Features II, III.} We start again with feature III. As shown in 
\autoref{fig:main_scheme}~(d), the sideband 
transitions are formed by two-photon processes 
with $\hat H_d^2$. On the other hand, we know from 
the unperturbed solution that in the laboratory 
frame the two transitions forming the avoided 
crossing are $10 - 02$ (one-photon) and $12/3$ 
(three-photon). This means that there should be a 
smooth transformation between these 1-, 2- and 3-photon 
processes when the system approaches the resonant 
point where $\alpha_2 + 2 \omega_{2} = 2\omega_1$. Let us consider hypothetical two-photon transitions $(10 
- 02)/2$ and $12/2$. In the frame rotating with 
the first transmon like in 
\autoref{fig:main_scheme}~(c) when $\Omega_1$ = 
0, their 
frequencies are
\begin{equation}
\begin{aligned}
\omega_{(10-02)/2} &= (\alpha_2 + 2 \omega_{2} - \Delta_1)/2,\\
 \omega_{12/2} &= (\alpha_2 + 2 \omega_{2} + \Delta_1)/2.
\end{aligned}
\label{eq:two-photon_lab}
\end{equation}
When the first transmon becomes dressed by $\Omega_1 \neq 0$, its splitting $\Delta_1$ changes to $\Omega^R_1 =\sqrt{\Omega_{1}^2 + \left(\omega_{1} - \omega_{d}\right)^{2}}$. Substituting this new splitting into the equations above we find that $\omega_{(10-02)/2}$ and $\omega_{12/2}$ are exactly equal to the two-photon sideband frequencies $\omega_1 \pm \Omega_1^R/2$ established in the previous section. Therefore, it is logical to use them to model the splitting behaviour beyond the resonant point.

@@

When $\Omega_1 = 0$, these equations yield indentical pairs of solutions due to the properties of the modulus $|\omega_1 - \omega_d|$. Substituting \autoref{eq:two-photon} into \autoref{eq:two-photon_lab}, we obtain the frequencies and identify them as the three-photon and single-photon transition frequencies in the laboratory frame:
\begin{equation}
\omega_d = \begin{cases} \frac{\alpha_2}{3} + \frac{2 \omega_{2}}{3} + \frac{\omega_{1}}{3}, \\ \alpha_2 + 2 \omega_{2} - \omega_{1}.\end{cases}
\end{equation}
When $\Omega_1 \neq 0$, we obtain the following solutions:
\begin{equation}
\omega_d = \frac{2 \alpha_2}{3} + \frac{4 \omega_{2}}{3} - \frac{\omega_{1}}{3} \pm \frac{\sqrt{3 \Omega_{1}^{2} + \left( \alpha_2 + 2 (\omega_{2} - \omega_{1})\right)^{2}}}{3}.
\label{eq:splitting_model}
\end{equation}
The minimal splitting between these lines is 
found at the resonant point and equals $\frac{2 
\sqrt{3}}{{3}} \Omega_1$. All these calculations 
can be repeated exactly for the feature II by 
swapping the transmons; in that case, the 
splitting will be $\frac{2 \sqrt{3}}{{3}} 
\Omega_2$.

@@

Continuing this logic, we can write down the resonance condition in the doubly-rotating frame when both transmons are dressed simultaneously:
\begin{equation}
\Omega_1^R \pm \Omega_2^R = 0.
\label{eq:zero-photon}
\end{equation}
Solving it for $\omega_d$, we obtain the 
generalization of \autoref{eq:topo_1} and 
\autoref{eq:topo_1_inv}:
\begin{equation}
\omega_d = \frac{\omega_{1} + \omega_{2}}{2} + \frac{\Omega_{1}^{2} - \Omega_{2}^{2}}{ 2\left(\omega_{1} - \omega_{2}\right)}
\label{eq:topo_comm}
\end{equation}

@@

\section{Standard Autler-Townes effect for a three-level $\Xi$ atom} \label{sec:3-level-at}

@@

The choice of zero-order state vectors $\ket{N^0}$ from a degenerate subspace is arbitrary because any linear combination of basis vectors $\ket{n}$ from this subspace will satisfy the unperturbed Schrödinger equation. However, if we demand the \textit{change} of $\ket{N^0}$ to be small under the perturbation $\hat V_J$, they become determined and are given by diagonalization of $\hat V_J$ in the degenerate subspace. Unfortunately, $\hat V_J$ is zero in both our subspaces, so technically any choice of zero-order states will diagonalize $\hat V_J$. In other words, the degeneracy is not lifted in the first-order, and thus we have diagonalize the matrix\cite{landau2013quantum}
\begin{equation}
	M_{nn'} = \sum\limits_{m}\frac{V_{ nm}V_{mn^\prime}}{E_n-E_m}.
\end{equation}
Here, $\ket{n}$ and $\ket{n'}$ are the basis 
states from the degenerate subspace with energy 
$E_n$, and $V_{mn} = \bra{m} \hat  V_J \ket{n}$. 
The sum is over all other zero-order states 
$\ket{m}$ outside the degenerate subspace.
